%!TEX TS-program = xelatex
\documentclass[print]{friggeri-cv}

% Compress itemize
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
  
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}~}

\begin{document}
\header{Christopher Li}
       {}


% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    \href{mailto:licy@usc.edu}{licy@usc.edu}
    \href{http://chris.topher.li}{http://chris.topher.li}
  \section{Languages}
    C/\Cplusplus/Objective-C
    Python
    Ruby
    JavaScript
    \textsc{html}, \textsc{css}
    {\sc Matlab}
    Verilog
    SQL
    \LaTeX
  \section{Tools}
    *nix Administration
    Adobe Illustrator
    Subversion
    Git
    Bash
\end{aside}

\section{Education}

\education
  {University of Southern California}
  {Los Angeles}
  {may 2013}
  {
  B.S. Electrical Engineering (hardware software emphasis) \Space GPA: 3.7
  }

\vspace{-1.0em}
\begin{entrylist}
  \project {Courses}
  {
  Data Structures\Space Operating Systems\Space User Interface Design\\Embedded Systems
  }
  
  \project{Awards}
  {
    USC Presidential Scholarship \hfill \textit{2009--present}
    
    Viterbi School of Engineering Dean's List \hfill \textit{6 semesters}
    
    W.V.T. Rusch Engineering Honors Program \hfill \textit{2009--present}
  }
  
  \project{Societies}
  {
    Eta Kappa Nu (HKN), Tau Beta Pi, IEEE
  }
  
\end{entrylist}

\section{Work Experience}

\workexperience
  {Intern}
  {Apple}
  {summer 2012}
  {
  Designed and implemented a distributed, fault-tolerant system for running RF tests.
  \begin{itemize*}
    \item Increased autonomous running time from minutes to hours, up to 80x.
    \item Implemented a web interface to control tests remotely, allowing for overnight jobs.
    \item Created a graphical interface with a data visualizer for antenna engineers.
  \end{itemize*}
  }

\workexperience
  {Paid Researcher}
  {USC iLab}
  {2011--present}
  {
  Granted Rose Hills Fellowship to work on hardware and software for autonomous vehicles for both the iLab and USC Aerial Robotics.
  \begin{itemize*}
    \item Redesigned GUI for the USC iLab's robotics framework, allowing for live collaboration with multiple users over the web.
    \item Led a migration to git for versioning, increasing organization.
    \item Implemented serial communication between microcontroller and onboard computer.
    \item Taught new members electronic design and construction as electrical team lead.
  \end{itemize*}
  }

\workexperience
  {User Interface Developer}
  {BountyBuy}
  {summer 2011}
  {
  Responsible for implementation of designs to Haml and Sass, JavaScript interactions, and Ruby on Rails features.
  \begin{itemize*}
    \item Refactored Rails unit and integration tests, halving test times.
    \item Redesigned user interaction for entering locations to provide visual feedback.
  \end{itemize*}
  }  

\section{Personal Projects}

\begin{entrylist}
  \project
    {Maxel}
    {A multi-threaded download accelerator written using Cocoa and libcurl. Maxel concurrently downloads a file by opening multiple HTTP connections to different segments in the file.}
  \project
    {Trollicons}
    {Rage icons for the most popular IM clients. A Ruby script makes deployment and generation of packages quick and easy. Over 20,000 downloads.}
  \project
    {SevenServers}
    {Web-based, social SFTP client. Users can add SFTP servers, add friends, and pool their servers into a single virtual storage space.}
\end{entrylist}

\nopagebreak

\end{document}
