%!TEX TS-program = xelatex
\documentclass[print]{friggeri-cv}

% Compress itemize
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
  
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}

\begin{document}
\header{Christopher Li}
       {}


% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    \href{mailto:licy@usc.edu}{licy@usc.edu}
    \href{http://chris.topher.li}{http://chris.topher.li}
  \section{Languages}
    C/\Cplusplus/Objective-C
    Python
    Ruby
    JavaScript
    {\sc Matlab}
    Verilog
    SQL
  \section{Tools}
    *nix Administration
    Adobe Illustrator
    Subversion
    Git
    Bash
\end{aside}

\section{Education}

\education
  {University of Southern California}
  {Los Angeles}
  {may 2013}
  {
  B.S. Electrical Engineering (hardware software emphasis) \Space GPA: 3.7
  }

\vspace{-1.0em}
\begin{entrylist}
  \project
    {Courses}
    {Data Structures\Space Operating Systems\Space User Interface Design\Space Embedded Systems Design Lab}
  
  \project{Honors}
  {
    USC Presidential Scholarship 2009--present
  
    Viterbi School of Engineering Dean's List 2009--present
  
    W.V.T. Rusch Engineering Honors Program 2009--present
  }
  
  \project{Societies}
  {
    Eta Kappa Nu (HKN), Tau Beta Pi, IEEE
  }
  
\end{entrylist}

\section{Work Experience}

\workexperience
  {OTA/Antenna Design Intern}
  {Apple}
  {summer 2012}
  {
  Used Python to make a distributed, fault-tolerant framework for automating RF test equipment. Worked with overseas equipment vendor to develop their automation interface. Wrote data visualizer and helped centralize test data.
  \begin{itemize*}
    \item Increased autonomous running time by up to 80x.
  \end{itemize*}
  }
\workexperience
  {Paid Research}
  {USC iLab}
  {2011--present}
  {
  Granted Provost Fellowship to create a GUI for the Neuromorphic Robotics Toolkit for the USC iLab. Designed and manufactured components for an autonomous land vehicle. Wrote microprocessor software for control.
  \begin{itemize*}
    \item Increased running time by adding automatic low-battery shutoff.
  \end{itemize*}
  }
\workexperience
  {Paid Research}
  {USC Aerial Robotics}
  {2009--present}
  {
  Granted Rose Hills Fellowship to write navigation software with ROS in \Cplusplus\ and Python for an autonomous quadrotor helicopter. Responsible for low-level control with an Arduino and serial communication. Electrical Team Lead since Fall 2012.
  \begin{itemize*}
    \item Increased organization by leading a migration to git for versioning.
    \item Reduced quadrotor weight by 5\% with a new power distribution board.
    \item Placed 5th of 13 teams at the AUVSI International Aerial Robotics Competition.
  \end{itemize*}
  }

\section{Personal Projects}

\begin{entrylist}
  \project
    {Nimbus}
    {File system for CloudApp, written using FUSE. Successfully funded through Kickstarter.}
  \project
    {Maxel}
    {A multi-threaded download accelerator written using Cocoa and libcurl.}
  \project
    {Trollicons}
    {Rage icons for the most popular IM clients. A custom rake script makes deployment and generation of packages quick and easy. Over 20,000 downloads.}
  \project
    {SevenServers}
    {Web-based, social S/FTP client. Written in Ruby on Rails.}
\end{entrylist}

\nopagebreak

\end{document}
